Long term cloud enhancement events of global solar irradiance over Thessaloniki, Greece

### 2024-06-11 article/article.Rmd
Commit 2024-06-11 22:14

!!! monthly weithe !!!

Another interesting aspect of the CE events is their distribution within the year.
Figure\nobreakspace{}\ref{fig:relative-month-occurrences} shows the monthly box 
and whisker plot of the CE number of occurrence normalized with the highest median value,
that occurs on June.  Although the number of occurrences has a wide spread throughout
the study period, the most active period of CE occurrences is during May and June.
During the Winter (December -- February) the CE cases are about $25\,\%$ of the maximum.
For the rest months, the occurrences gradually ramp between the maximum and minimum.
This seasonality is a combinations of the clouds occurrences, and the relevant
position of the sun during each season of the year. Unfortunately, the lack of detailed data on cloud
formation, type and location is not allowing further analysis.

>>>>

!!! monthly weigth !!!

Another interesting aspect of the CE events is their distribution within the year.
Figure\nobreakspace{}\ref{fig:relative-month-occurrences} shows the monthly box and
whisker plot of the CE number of occurrence normalized with the highest median value,
that occurs on June.  Although CE events are present  throughout the year, the most
active period  is during May and June.  During the winter (December -- February) the
number of CE cases is about $25\,\%$ of the maximum.  For the rest months, the
occurrences gradually ramp between the maximum and minimum.  This seasonality is a
combinations of the clouds occurrences, and the relevant position of the sun during
each season of the year. Unfortunately, the lack of detailed data on cloud formation,
type and location is not allowing further analysis.
